Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-24 snippets/data_exploration/data_exploration_tmp.Rmd
uniformity and EU

require('ellipse')
require('ggplot2')
require('reshape2')
require('plyr')
source('~/Desktop/data/svn/programming/R/helpers/helpers.R')
source('~/Desktop/data/svn/vagueness-games/data-analysis.R')

@@

plot.language.byindex = function(dataFrame,rowindex){
  plot.language(dataFrame[rowindex,]$Speaker.strategy.file,
                dataFrame[rowindex,]$Hearer.strategy.file)
}

plot.language.MinMaxProperty = function(dataFrame,colindex){
  show(names(dataFrame)[colindex])
  show(summary(dataFrame[,colindex]))
  p = arrangeGrob(plot.language.byindex(dataFrame,which.min(dataFrame[,colindex])),
                  plot.language.byindex(dataFrame,which.max(dataFrame[,colindex])))
}

>>>>

require('ellipse')
require('ggplot2')
require('reshape2')
require('plyr')
source('~/Desktop/data/svn/programming/R/helpers/helpers.R')
source('~/Desktop/data/svn/vagueness-games/data-analysis.R')
source('~/Desktop/data/svn/vagueness-games/helper_functions.R')

@@
